Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-10 paper.qmd
optimize the code of Figure 18

@@

right_top_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  ggtitle("(a)") +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Reds 2") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.31,
                                  size = 12))

#img_middle <- c(1069, 4604, 3579)
img_middle <- c(130, 2091, 7795)

@@

middle_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  ggtitle("(b)") +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Greens 3") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.31,
                                  size = 12))

#img_right_bottom <- c(1695, 5338, 2805)
img_right_bottom <- c(2035, 7708, 7710)

@@

right_bottom_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  ggtitle("(c)") +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Purples 2") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.31,
                                  size = 12))

#img_error_outside <- c(3554, 501, 4422, 6860, 3869, 1529, 4916, 6144)
#img_error_outside <- c(501, 1529, 6144)
img_error_outside <- c(999, 3650, 4916)

@@

imge_error_sample_outside <- pixels_gathered_outside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  ggtitle("(d)") +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0.31,
                                  size = 12))

@@

imge_error_sample_inside <- pixels_gathered_inside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 9) +
  ggtitle("(e)") +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = 0,
                                  size = 12))

>>>>

```{r}
#| label: plot-digit

plot_digit_img <- function(digit_df, palette, title_text, hjust, ncol = 4) {

  ggplot(data = digit_df, aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = ncol) +
  ggtitle(title_text) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = palette) +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(hjust = hjust,
                                  size = 12))

@@

right_top_img <- plot_digit_img(pixels_gathered_within, palette = "Reds 2", title_text = "(a)", hjust = 0.31)

img_middle <- c(130, 2091, 7795)

@@

middle_img <- plot_digit_img(pixels_gathered_within, palette = "Greens 3", title_text = "(b)", hjust = 0.31)

img_right_bottom <- c(2035, 7708, 7710)

@@

right_bottom_img <- plot_digit_img(pixels_gathered_within, palette = "Purples 2", title_text = "(c)", hjust = 0.31)

img_error_outside <- c(999, 3650, 4916)

@@

imge_error_sample_outside <- plot_digit_img(pixels_gathered_within, palette = "Grays", title_text = "(d)", hjust = 0.31)

@@

imge_error_sample_inside <- plot_digit_img(pixels_gathered_inside, palette = "Grays", title_text = "(e)", hjust = 0, ncol = 9)
